Selecting and ranking interesting pairs of cyclic temporal granularities

### 2021-02-11 comparison_perm_scalar.Rmd
methodology updated
some figures update

G21 <- read_rds("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_Gamma21.rds")

@@

@@

all_data_scalar <- 
```

>>>>

G21 <- read_rds(here("simulations/raw/null_design_quantrans/data-agg/all_data_wpd_Gamma21.rds"))

@@

G21 %>% 
  ggplot(aes(x=log(nx*nfacet), y = (value - slope*log(nx*nfacet)))) +
  geom_point() + stat_summary(fun=mean, geom="line", aes(group=1), color = "blue") + 
  xlab("$wpd_norm =  wpd_raw - slope*log(nx*nfacet)$")

@@

#all_data_scalar <- 
```

### 2021-02-11 paper/main.Rmd
some figures update

## Size

@@

plot_mmpd_null_grid(data_N01_samp, data_N01_obs)

@@

@@

# check transformation and scalar approaches are same

```{r scalar-approach}
set.seed(7777)
all_data <- read_rds("paper/sim_table/all_data_scalar.rds")
sm_cust_data <- read_rds("paper/data/sm_cust_data.rds")
set.seed(7777)
sm_unique_cust <- sm_cust_data %>% distinct(customer_id)
sm_cust_samp <- sm_cust_data %>% 
  #filter(customer_id %in% sm_30) %>% # for demo show 30 customers
  #filter(year(reading_datetime) == 2012) %>% #for demo just show one column
  as_tsibble(index = reading_datetime,
             key = customer_id) %>% 
  create_gran("day_week") %>% 
  create_gran("hour_day")

@@

hc = stats::hclust(d,method="complete")
plot(hc)
groups<-cutree(hc, k=4)

@@

ggpubr::ggscatter(all_data_cluster,
                  x = "Dim.1",
                  y = "Dim.2", 
                  label = rownames(mds),
                  color = "groups",
                  size = 1,
                  repel = TRUE)

@@

@@

```{r}
raw_data <- sm_cust_data %>% 
  left_join(mds, by = "customer_id")

p1 <- raw_data %>% 
  filter(groups==1) %>% 
  ggplot() + 
  geom_line(aes(x = reading_datetime,
            y = general_supply_kwh)
  )

p2 <- raw_data %>% 
  filter(groups==2) %>% 
  ggplot() + 
  geom_line(aes(x = reading_datetime,
            y = general_supply_kwh)
  )

p3 <- raw_data %>% 
  filter(groups==3) %>% 
  ggplot() + 
  geom_line(aes(x = reading_datetime,
            y = general_supply_kwh)
  )
library(patchwork)
p1/p2/p3

@@

```{r}
raw_data <- sm_cust_data %>% 
  left_join(mds, by = "customer_id")

p1 <- raw_data %>% 
  filter(groups==1) %>% 
  prob_plot("day_week",
            "hour_day",
            response = "general_supply_kwh",
            plot_type = "quantile",
            symmetric = FALSE
)

p2 <- raw_data %>% 
  filter(groups==2) %>% 
  prob_plot("day_week",
            "hour_day",
            response = "general_supply_kwh",
            plot_type = "quantile",
            symmetric = FALSE
)

p3 <- raw_data %>% 
  filter(groups==3) %>% 
  prob_plot("day_week",
            "hour_day",
            response = "general_supply_kwh",
            plot_type = "quantile",
            symmetric = FALSE
)
library(patchwork)
p1
p2
p3

@@

### Advantage over taditional feature based methods

>>>>

@@

#plot_mmpd_null_grid(data_N01_samp, data_N01_obs)

@@

# Plot and color by groups
q1 <- ggpubr::ggscatter(mds, x = "Dim.1", y = "Dim.2", 
          label = rownames(mds),
          color = "groups",
          palette = "jco",
          size = 1, 
          ellipse = TRUE,
          ellipse.type = "convex",
          repel = TRUE)

@@

- check transformation and scalar approaches are same

```{r scalar-approach}
set.seed(7777)
all_data <- read_rds(here("paper/sim_table/all_data_scalar.rds"))
sm_cust_data <- read_rds(here("paper/data/sm_cust_data.rds"))
set.seed(7777)
sm_unique_cust <- sm_cust_data %>% distinct(customer_id)
sm_cust_samp <- sm_cust_data %>% 
  #filter(customer_id %in% sm_30) %>% # for demo show 30 customers
  #filter(year(reading_datetime) == 2012) %>% #for demo just show one column
  as_tsibble(index = reading_datetime,
             key = customer_id) %>% 
  create_gran("day_week") %>% 
  create_gran("hour_day")

@@

hc = stats::hclust(d,method="complete")
#plot(hc)
groups<-cutree(hc, k=3)

@@

q2 <- ggpubr::ggscatter(all_data_cluster,
                  x = "Dim.1",
                  y = "Dim.2", 
                  label = rownames(mds),
                  color = "groups",
                  size = 1,
                  repel = TRUE)

q1 + q2
```

@@

```{r, echo = FALSE}

@@

```{r linear}
raw_data <- sm_cust_data %>% 
  left_join(all_data_cluster, by = "customer_id")

p1 <- raw_data %>% 
  filter(groups==1) %>% 
  ggplot() + 
  geom_line(aes(x = reading_datetime,
            y = general_supply_kwh)
  ) + ggtitle("Group 1")

p2 <- raw_data %>% 
  filter(groups==2) %>% 
  ggplot() + 
  geom_line(aes(x = reading_datetime,
            y = general_supply_kwh)
  ) + ggtitle("Group 2")

p3 <- raw_data %>% 
  filter(groups==3) %>% 
  ggplot() + 
  geom_line(aes(x = reading_datetime,
            y = general_supply_kwh)
  ) + ggtitle("Group 3")
library(patchwork)
p1/p2/p3

@@

```{r gravitas}
raw_data <- sm_cust_data %>% 
  left_join(all_data_cluster, by = "customer_id")

p1 <- raw_data %>% 
  filter(groups==1) %>% 
  prob_plot("day_week",
            "hour_day",
            response = "general_supply_kwh",
            plot_type = "quantile",
            symmetric = FALSE
)  + ggtitle("Group 1")

p2 <- raw_data %>% 
  filter(groups==2) %>% 
  prob_plot("day_week",
            "hour_day",
            response = "general_supply_kwh",
            plot_type = "quantile",
            symmetric = FALSE
)  + ggtitle("Group 2")

p3 <- raw_data %>% 
  filter(groups==3) %>% 
  prob_plot("day_week",
            "hour_day",
            response = "general_supply_kwh",
            plot_type = "quantile",
            symmetric = FALSE
)  + ggtitle("Group 3")

library(patchwork)
p1
p2
p3

@@

### Advantage over taditional feature based clustering methods
